### 2017-01-22 thesis/latex/thesis.tex
Add all thesis figures to root figures directory and make thesis build.

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
  \caption{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{diffusion_vs_dynein}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/retrograde_transport.jpg}
  \caption{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport. Modified from \cite{valetoolbox}.}
  \label{retrograde-transport}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/mtbd-complex.png}
  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/diffusion_vs_dynein.png}
%%   \caption{Crystal structures of cytoplasmic dynein 1 and kinesin KIF5B (PDB IDs 4RH7 and 1BG2).}
%%   \label{kin_n_dyn}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/two-state-em-diagram}
%%   \caption{}
%%   \label{nuecleotide-state}
%% \end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/nucleotide-state-cycle}
%%   \caption{}
%%   \label{nucleotide-state-diagram}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/ob_fig.pdf}
  \caption{Spatial representation of onebound model.}
  \label{ob_fig}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/code-bothbound.pdf}
  \caption{Definition of equilibrium angles.}
  \label{bb_fig}
\end{figure}

@@

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{equipartition_agreement}
%% \end{figure}

@@

\subsubsection{Equipartition theorem obeyed}
%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{fig:equipartition_agreement}
%% \end{figure}

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
  \caption{Plot comparing the diffusion rate of a 140kD protein with a diffusion consant $D = .2 \mu m^2/s$ with a dynein motor travelling at 100nm/s.}
  \label{diffusion_vs_dynein}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/retrograde_transport.jpg}
  \caption{Mechanism of dynein localization to axon tips, or growth cones, in retrograde transport mediated by kinesin anterograde transport. Modified from \cite{valetoolbox}.}
  \label{retrograde-transport}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/dynein-artist-rendition.jpg}
  \caption{Artist rendition of the dynein motor bound to a microtubule. One monomer is bound to the MT, and one is raised up. Modified. Source: Lander Lab, The Scripps Research Institute.}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mtbd-complex.png}
  \caption{Crystal structure of the MTBD-MT complex. Modified from Redwine \textit{et. al} \cite{redwineMTBDcomplex}.}
  \label{dynein-artist-rendition-2}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/diffusion_vs_dynein.png}
%%   \caption{Crystal structures of cytoplasmic dynein 1 and kinesin KIF5B (PDB IDs 4RH7 and 1BG2).}
%%   \label{kin_n_dyn}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/mechanochemical-cycle.jpeg}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

@@

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/two-state-em-diagram}
%%   \caption{}
%%   \label{nuecleotide-state}
%% \end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \includegraphics[width=.65\textwidth,keepaspectratio]{../../figures/nucleotide-state-cycle}
%%   \caption{}
%%   \label{nucleotide-state-diagram}
%% \end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/ob_fig.pdf}
  \caption{Spatial representation of onebound model.}
  \label{ob_fig}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../../figures/code-bothbound.pdf}
  \caption{Definition of equilibrium angles.}
  \label{bb_fig}
\end{figure}

@@

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{equipartition_agreement}
%% \end{figure}

@@

\subsubsection{Equipartition theorem obeyed}
%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{fig:equipartition_agreement}
%% \end{figure}
